---
title: "My Presentation"
subtitle: "A subtitle"
author: 
  - Aaron Gullickson, University of Oregon
output:
  ioslides_presentation:
    css: presentation_template.css
    widescreen: yes
    incremental: true
---

<!-- Get rid of page numbering in footer-->
<style type="text/css">
slides > slide:not(.nobackground):after {
  content: '';
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(knitr)
library(texreg)
library(ggplot2)
```

## Basic Slide | Is this a good subtitle?
<div class="footer">
<body>Aaron Gullickson, My Presentation</body>
</div>

This is an example of a basic slide with just text and bullet points on it. Note the custom footer that can be applied. 

- Bullet 1
- Bullet 2
- Bullet 3

## Smaller Slide {.smaller}
<div class="footer">
<body>Aaron Gullickson, My Presentation</body>
</div>

Now I have applied the smaller attribute to the basic slide. 

This is an example of a basic slide with just text and bullet points on it. Note the custom footer that can be applied. 

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output
<div class="footer">
<body>Aaron Gullickson, My Presentation</body>
</div>

```{r cars, echo = TRUE}
summary(cars)
```

<div class="notes">
This is my *note*.

- It can contain markdown
- like this list

</div>


## Slide with table 
<div class="footer">
<body>Aaron Gullickson, My Presentation</body>
</div>

```{r}
tab <- round(100*prop.table(apply(Titanic, c(3,4), sum),1),1)
kable(tab, caption="Survival on the Titanic")
```

## Slide with Plot
<div class="footer">
<body>Aaron Gullickson, My Presentation</body>
</div>

<!-- When making a plot, you can change the width and height to size it as appropriate but be sure to also change the out.width and out.height by a factor of 100 x the heigh and width to maintain proper resolution-->


```{r echo=FALSE, fig.width=7, fig.height=5, out.width='700px', out.height='500px', dpi=300, fig.align='center', dev.args = list(bg = 'transparent')}
# I find it useful to reduce the top and right margins of the base plot in order to use more real estate
# since title will be in the slide title
par(mar=c(5,4,0.5,0.5))
plot(pressure)
```

## Slide with ggplot
<div class="footer">
<body>Aaron Gullickson, My Presentation</body>
</div>

<!-- For ggplot, you need to specify a transparent backgroun in the theme options as well-->


```{r echo=FALSE, fig.width=7, fig.height=5, out.width='700px', out.height='500px', dpi=300, fig.align='center', dev.args = list(bg = 'transparent'), warning=FALSE, message=FALSE}
ggplot(pressure, aes(x=temperature, y=pressure))+
  geom_smooth()+
  geom_point()+
  theme_bw()+
  theme(plot.background = element_rect(fill = "transparent",colour = NA))
```

## Slide with a regression model using texreg
<div class="footer">
<body>Aaron Gullickson, My Presentation</body>
</div>

<div class="texreg">
```{r echo=FALSE, results="asis", warning=FALSE, message=FALSE}
model1 <- lm(Fertility~Agriculture, data=swiss)
model2 <- update(model1, .~.+Education)
model3 <- update(model2, .~.+Catholic)
htmlreg(list(model1, model2, model3),
        custom.coef.names=c("Intercept",
                            "Percent in agriculture",
                            "Percent with primary education",
                            "Percent Catholic"),
        custom.gof.names = c("R-squared","N"),
        caption="OLS regression models predicting fertility index in Swiss cantons",
        caption.above=TRUE,
        digits=2,
        star.symbol='&#42;',
        custom.note = "%stars. Standard errors in parenthesis.",
        include.adjrs=FALSE, include.rmse=FALSE,
        doctype = FALSE)
```
</div>

---- 
<div class="footer" style="top:575px;"> 
<body>Aaron Gullickson, My Presentation</body>
</div>

This is a slide with no title. Sometimes useful if you want to take up the whole space with a graph. Note that you have to make a slight change to the footer in order for it to show up properly. 
